A comprehensive framework to capture the arcana of neuroimaging analysis

### 2018-10-30 manuscript/manuscript.tex
added code for floating listings (but then disabled them again)

\usepackage{natbib}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{color}

@@

\lstset{
%    captionpos=b,                    % sets the caption-position to bottom
    language=Python,                 % the language of the code
    showstringspaces=false,          % underline spaces within strings only
    stringstyle=\color{stringcolour},     % string literal style
    commentstyle=\color{commentcolour},    % comment style
    keywordstyle=\color{keywordcolour}\bfseries,       % keyword style
}

>>>>

\usepackage{float}
\usepackage{natbib}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{color}

@@

\lstset{
    captionpos=b,                    % sets the caption-position to bottom
    language=Python,                 % the language of the code
    showstringspaces=false,          % underline spaces within strings only
    stringstyle=\color{stringcolour},     % string literal style
    commentstyle=\color{commentcolour},    % comment style
    keywordstyle=\color{keywordcolour}\bfseries,       % keyword style
    float
}

\newfloat{lstfloat}{htbp}{lop}
\floatname{lstfloat}{Listing}
\def\lstfloatautorefname{Listing}
